Copulas and their potential for ecology

### 2019-06-25 Paper.Rmd
submitted this version to Ecological Monographs yesterday
changed an erroneous grant number

@@

\noindent \emph{The number of words in the abstract:}

@@

We thank the many contributors to the large datasets we used; D. Stevens and P. Verrier for data 
extraction; and Joel E. Cohen, David Tilman, Lauren Hallet, Jonathan Walter, Thomas 
Anderson, and Lei Zhao for helpful suggestions. We thank James Bell of the Rothamsted Insect Survey 
(RIS). 
The RIS, a UK Capability, is funded by the Biotechnology and Biological Sciences Research Council 
under the Core Capability Grant BBS/E/C/000J0200. SG, LWS and DCR were partly funded by US National 
Science Foundation grants 0075516 and 1442595 and the James S McDonnell Foundation.

@@

@@

<!--\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{1pt}
\noindent
\sloppy-->

@@

>>>>

\raggedright
\setlength\parindent{2em}
\setlength{\parskip}{6pt}

@@

\noindent \emph{The number of words in the abstract:} 266

@@

We thank the many contributors to the large datasets we used; D. Stevens and P. Verrier for data 
extraction; and Joel E. Cohen, David Tilman, Lauren Hallet, Jonathan Walter, Thomas 
Anderson, and Lei Zhao for helpful suggestions. We thank James Bell of the Rothamsted Insect Survey 
(RIS). 
The RIS, a UK Capability, is funded by the Biotechnology and Biological Sciences Research Council 
under the Core Capability Grant BBS/E/C/000J0200. SG, LWS and DCR were partly funded by US National 
Science Foundation grants 1714195 and 1442595 and the James S McDonnell Foundation.

@@

\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{1pt}
\noindent
\sloppy

@@

@@

\setlength{\parindent}{0in}
\setlength{\leftskip}{0in}
\setlength{\parskip}{6pt}
